A comparative risk assesment of U.S. regional active transport using the ITHIM model

### 2016-10-05 manuscript/manuscript.tex
Edits to state-wise manuscript
Still working on figures for Maggie K.

\section{Summary:}
\col[blue]{While increased active transportation, primarily cycling
  and walking, is often held up as a goal for improved public health —
  via reduced chronic disease, improved air quality, and reductions in
  greenhouse gas emissions --- obtaining estimates for the quantiative
  impacts of such shifts remains infrequent, if not altogether
  absent from related policy action. Using U.S. metropolitan counties from the 10 regions defined
  by the U.S. Department of Health and Human Services (HHS1-10) we perform
  a comparative risk analysis between each regions and national
  averages as the baseline.  We investigated the reduced chronic
  disease burden of ($x$, $y$, $z$ outcomes) from increased physical
  activity from population shifts in the amount of biking and walking
  doen for transport.  Our methods employ the Integrated Transport and
  Health Impacts Model (ITHIM) informed by regional travel parameters
  using the National Household Transportation Survey, non-travel
  activity metircs from the American Time Use Survey, and baseline
  Disease burden from the Centers for Disease Control and Prevention's
  WONDER database.  Our findings show that the West coast and the
  Northeast of the U.S. have travel patterns that, if mirrored by the
  nation, would save the U.S. thousands to hundreds of thousands
  DALYs.}

@@

@@

\col{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do
  eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim
  ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut
  aliquip ex ea commodo consequat. Duis aute irure dolor in
  reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla
  pariatur. Excepteur sint occaecat cupidatat non proident, sunt in
  culpa qui officia deserunt mollit anim id est laborum. Lorem ipsum
  dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor
  incididunt ut labore et dolore magna aliqua.}

\col{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do
  eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim
  ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut
  aliquip ex ea commodo consequat. Duis aute irure dolor in
  reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla
  pariatur. Excepteur sint occaecat cupidatat non proident, sunt in
  culpa qui officia deserunt mollit anim id est laborum.}

@@

@@

\begin{figure}[t]
    \centerline{\includegraphics[width=0.5\textwidth]{./figures/fig1}}
    \centerline{\includegraphics[width=0.5\textwidth]{./figures/fig2}}
    \caption{Change in total national DALYs for each regional
      transportation estimates.}\label{dalyFigure}
\end{figure}

>>>>

\section{Summary:}
\col[blue]{While increased active transportation, primarily cycling
  and walking, is often held up as a goal for improved public health —
  via reduced chronic disease, improved air quality, and reductions in
  greenhouse gas emissions — obtaining estimates for the quantiative impacts of such shifts remains infrequent, if not altogether absent from related policy action. Using U.S. metropolitan counties from seven states we perform a comparative risk analysis between each regions and national averages as the baseline.  We employ a portion of the Integrated Transport and Health Impacts Model (ITHIM) to investigate the reduced chronic disease burden of (x,y,z outcomes) from changing levels of physical activity with population shifts in the amount of biking and walking done for transport. The analysis is informed by regional travel parameters from the National Household Transportation Survey, non-travel activity metrics from the American Time Use Survey, and baseline disease burden from the Centers for Disease Control and Prevention's WONDER database and the Global Burden of Disease dataset.  Our findings show that the California and New York State have travel patterns that, if mirrored by the nation, would save the U.S. upwards of fifty thousand disability adjusted life years.}

@@

\col{Regular exercise has been shown to provide health benefits in terms of chronic disease prevention \cite{warburton2006}, cognitive function \cite{hillman2008}, and overall well being and satisfaction with life \cite{maher2013}. Still only half of Americans obtain the recommended levels of aerobic activity, which is 2.5 hours per week. There is considerable variability in the attainment of this goal by location within the country. Supportive local built and policy environments are important determinants of population-level activity patterns. Particularly, as they facilitate and foster routine moderate physical activity, such as walking, local decissions on design and policy can play a huge role in the Nation's health.}

\col{To better understand the potential for attainable shifts in transportation behavior across the US, we employed a comparative risk assessment methodology to compare national averages for time spent walking and cycling for transport to those of specific states. Our estimates can provide an important evidence base to encourage new construction, retrofits, land use policy, and programatic funding to support active transportation. Particularly in places with poor attainmnet of the physical activity guidelines, such investments can be importnat pieces of lareger population health interventions that have effective and long-lasting impacts. }

@@

@@

\begin{figure}[t]
    \centerline{\includegraphics[width=0.5\textwidth]{./figures/fig1}}
    \caption{Map of HHS Regions and metropolitan areas}\label{HHSmap}
\end{figure}

@@

\begin{figure}[t]
  \centerline{\includegraphics[width=0.5\textwidth]{./figures/fig3.pdf}}
    \caption{Mean travel time by mode (walking/cycling) for each of
      the four regions with a decrease in DALYs
      $(\textrm{HHS01},\textrm{HHS02},\textrm{HHS09},\textrm{HHS10})$. The
      national means are displayed on the far right.  These four
      regions correspond to New England/NewYork and the West
      Coast.}\label{meanMatrices}
\end{figure}
